Towards Spherical Robots For Mobile Mapping In Human Made Environments\tnoteref{mytitlenote}

### 2021-05-13 Latex/sections/registration.tex
Replace rigid registration with coarse prere-registration; added info about pre-registration

Consider a line scan as the smallest chunk of range data we obtain from the scanner device driver.
In the case of a SICK LMS1xx it is a line, and in case of a Livox scanner it has a flower shape.
More details are provided in the following sections.
We start with transforming each line scan into the project coordinate system, which is defined by the pose of the first acquired line scan.
%
For map improvement, the individual scans need to be registered to another. 
We propose an algorithm that consists of multiple steps outlined in algorithm~\ref{algo:registration-algorithm}. 
Based on ideas described in~\cite{Borrmann2010} we first rigidly register the scans and then further improve the overall map by exploiting the fact that human-made environments often consist of planes. 
We then find the planes in the pre-registered point cloud and then optimize the poses associated with the scans to minimize the distance of all points to their respective planes.

\begin{algorithm}
    \SetAlgoLined
    \KwResult{A corrected map}
    1. Rigidly register the scans\;
    2. Extract planes from the registered map\;
    3. Further improve map by solving the optimization that minimizes the distance of all points to their respective planes\;
    \caption{Registration algorithm for man-made environments}
    \label{algo:registration-algorithm}
\end{algorithm}

\subsection{Rigid Registration}

\todo[inline]{Die Rigid Registration sollte kurz erwähnt werden. Welcher Algorithmus? Werden dafür Linescans zusammengefasst?}

@@

After having done the rigid registration, the scans are aligned well enough to make statements about the potential planes in the environment.
To find the planes in the environment, a Randomized Hough transform with an accumulator ball as described in~\cite{3DRESEARCH2011} is used. 
In the next subsection, the Hesse-normal form of the plane is required.
For an ideal plane the distance parameter $\rho_{\mathcal{P}_i}$ is computed via $\vec{n}_{\mathcal{P}_i}\cdot\vec{x}_i$, where $\vec{x}_i$ is an arbitrary point on the plane.
To find this point, we first define a convex hull that encloses the plane.
It is defined by the points that lie on the plane with the furthest distance to one another.
We then choose the center point of the convex hull of the plane as $\vec{x}_i$.

>>>>

Consider a line scan as the smallest chunk of range data we obtain from the scanner device driver.
In the case of a SICK LMS1xx it is a line, and in case of a Livox scanner it has a flower shape.
More details are provided in the following sections.
We start with transforming each line scan into the project coordinate system, which is defined by the pose of the first acquired line scan.
%
For map improvement, the individual scans need to be registered to another. 
We propose an algorithm that consists of multiple steps outlined in algorithm~\ref{algo:registration-algorithm}. 
Based on ideas described in~\cite{Borrmann2010} we first pre-register the scans and then further improve the overall map by exploiting the fact that human-made environments often consist of planes. 
We then find the planes in the pre-registered point cloud and then optimize the poses associated with the scans to minimize the distance of all points to their respective planes.

\begin{algorithm}
    \SetAlgoLined
    \KwResult{A corrected map}
    1. Pre-register the scans\;
    2. Extract planes from the registered map\;
    3. Further improve map by solving the optimization that minimizes the distance of all points to their respective planes\;
    \caption{Registration algorithm for man-made environments}
    \label{algo:registration-algorithm}
\end{algorithm}

\subsection{Pre-Registration}

We perform a coarse registration with the continuous-time SLAM approach from~\cite{REMSEN2013}.
This yields maps that can be used for plane registration and hence a point-to-plane correspondences base registration.

@@

After having done the pre-registration, the scans are aligned well enough to make statements about the potential planes in the environment.
To find the planes in the environment, a Randomized Hough transform with an accumulator ball as described in~\cite{3DRESEARCH2011} is used. 
In the next subsection, the Hesse-normal form of the plane is required.
For an ideal plane the distance parameter $\rho_{\mathcal{P}_i}$ is computed via $\vec{n}_{\mathcal{P}_i}\cdot\vec{x}_i$, where $\vec{x}_i$ is an arbitrary point on the plane.
To find this point, we first define a convex hull that encloses the plane.
It is defined by the points that lie on the plane with the furthest distance to one another.
We then choose the center point of the convex hull of the plane as $\vec{x}_i$.
